---
title: "R Syntax Drill — Week 01"
output:
  learnr::tutorial:
    progressive: false
    allow_skip: true
    css: "www/styles.css"
runtime: shiny_prerendered
tutorial:
  id: "r-syntax-drills-week-01"
  version: 1.0
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(shiny)
source("R/syntax_checkers.R")

gradethis::gradethis_setup(
  pass.praise = FALSE,
  fail.encourage = FALSE,
  fail.hint = FALSE
)

learnr::tutorial_options(
  exercise.timelimit = 10,
  exercise.reveal_solution = FALSE #,
  #exercise.warn_invisible = FALSE
)
```

```{r logging-start, context="server-start", include=FALSE}
library(httr2)
source("R/app_config.R")
source("R/question_manifest.R")
build_question_manifest()
source("R/logging.R")
register_logging_handlers(APP_CONFIG)
```

```{r identity-server, context="server", include=FALSE}
session$userData$identity <- shiny::reactiveVal(NULL)
session$userData$logging_status <- shiny::reactiveVal(
  list(ok = NA, message = "Enter your student ID before beginning.")
)

shiny::observeEvent(input$save_identity, {
  student_id <- trimws(input$student_id)
  student_name <- trimws(input$student_name)

  if (!grepl("^[A-Za-z0-9._@-]{2,100}$", student_id)) {
    session$userData$logging_status(list(
      ok = FALSE,
      message = "Enter a valid student ID (2–100 letters, digits, ., _, @, or -)."
    ))
    return()
  }

  session$userData$identity(list(
    student_id = student_id,
    student_name = student_name
  ))

  post_log_event(
    session,
    "identity_saved",
    data = list(label = "identity"),
    config = APP_CONFIG
  )
})

output$identity_status <- shiny::renderUI({
  status <- session$userData$logging_status()
  cls <- if (isTRUE(status$ok)) {
    "alert alert-success"
  } else if (identical(status$ok, FALSE)) {
    "alert alert-danger"
  } else {
    "alert alert-warning"
  }
  shiny::tags$div(class = cls, status$message)
})
```

## Before you begin

Your responses are graded immediately and recorded for your instructor. Enter the same student ID your course uses for grading.

```{r identity-ui, echo=FALSE}
shiny::wellPanel(
  shiny::textInput("student_id", "Student ID", placeholder = "e.g., abc123"),
  shiny::textInput("student_name", "Name (optional)", placeholder = "e.g., Ada Lovelace"),
  shiny::actionButton("save_identity", "Save identity"),
  shiny::br(), shiny::br(),
  shiny::uiOutput("identity_status")
)
```

## Drill 1: Assignment

Create a vector containing the integers 1 through 5. Assign it to `x` using the `<-` operator, then put `x` on the final line so its value is returned.

```{r assignment, exercise=TRUE, topic="vector_creation"}

```

```{r assignment-solution}
x <- 1:5
x
```

```{r assignment-check}
grade_this({
  if (!uses_call(.user_code, "<-")) {
    fail("Use the `<-` assignment operator.")
  }
  if (!identical(.result, 1:5)) {
    fail("`x` should contain the integers 1 through 5.")
  }
  pass("Correct: you used `<-` and created the requested vector.")
})
```

## Drill 2: Vector indexing

The vector `v` is provided. Return its **third element using single-bracket indexing** (`[ ]`).

```{r vector_index-setup, include=FALSE}
v <- c("alpha", "beta", "gamma", "delta")
```

```{r vector_index, exercise=TRUE, exercise.setup="vector_index-setup", topic="vector_indexing"}

```

```{r vector_index-solution}
v[3]
```

```{r vector_index-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single brackets: `v[3]`.")
  }
  if (uses_call(.user_code, "[[")) {
    fail("This drill is specifically asking for single-bracket indexing, not `[[ ]]`.")
  }
  if (!identical(.result, "gamma")) {
    fail("Return the third element of `v`.")
  }
  pass("Correct: single brackets select the requested vector element.")
})
```

## Drill 3: List extraction

The list `z` is provided. Extract its second element using **double-bracket extraction** (`[[ ]]`).

```{r list_extract-setup, include=FALSE}
z <- list(first = 10, second = c(20, 30), third = "done")
```

```{r list_extract, exercise=TRUE, exercise.setup="list_extract-setup", topic="list_indexing"}

```

```{r list_extract-solution}
z[[2]]
```

```{r list_extract-check}
grade_this({
  if (!uses_call(.user_code, "[[")) {
    fail("Use double brackets (`[[ ]]`) to extract one list element.")
  }
  if (!identical(.result, c(20, 30))) {
    fail("Extract the second element of `z`.")
  }
  pass("Correct: `[[ ]]` extracted the list element itself.")
})
```

## Drill 4: Named arguments

The vector `y` contains a missing value. Call `mean()` and explicitly use the named argument `na.rm = TRUE`.

```{r named_argument-setup, include=FALSE}
y <- c(2, 4, NA, 8)
```

```{r named_argument, exercise=TRUE, exercise.setup="named_argument-setup", topic="function_arguments"}

```

```{r named_argument-solution}
mean(y, na.rm = TRUE)
```

```{r named_argument-check}
grade_this({
  if (!uses_call(.user_code, "mean")) {
    fail("Call `mean()`.")
  }
  if (!call_has_named_arg(.user_code, "mean", "na.rm")) {
    fail("Explicitly name the `na.rm` argument.")
  }
  if (!isTRUE(all.equal(.result, mean(y, na.rm = TRUE)))) {
    fail("The mean should be calculated after removing the missing value.")
  }
  pass("Correct: you supplied `na.rm` as a named argument.")
})
```

## Drill 5: `$` extraction

Using the built-in `iris` data frame, return the first three values of `Sepal.Length`. Use `$` to select the column.

```{r dollar_extract, exercise=TRUE, topic="dataframe_indexing"}

```

```{r dollar_extract-solution}
iris$Sepal.Length[1:3]
```

```{r dollar_extract-check}
grade_this({
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` to select `Sepal.Length` from `iris`.")
  }
  if (!identical(.result, iris$Sepal.Length[1:3])) {
    fail("Return the first three values of `iris$Sepal.Length`.")
  }
  pass("Correct: you used `$` for data-frame column extraction.")
})
```

## Drill 6: Native pipe

Use the native R pipe `|>` at least once. Starting from `mtcars`, keep the rows where `cyl == 4` and return the number of resulting rows.

```{r native_pipe, exercise=TRUE, topic="piping"}

```

```{r native_pipe-solution}
mtcars |>
  subset(cyl == 4) |>
  nrow()
```

```{r native_pipe-check}
grade_this({
  if (!uses_token(.user_code, "|>")) {
    fail("Use the native R pipe, `|>`.")
  }
  if (!identical(.result, nrow(subset(mtcars, cyl == 4)))) {
    fail("Filter `mtcars` to four-cylinder cars and return the number of rows.")
  }
  pass("Correct: you used the native pipe and returned the requested count.")
})
```

## Drill 7: Define a function

Create a function called `double` that takes one argument `x` and returns `x * 2`. Put `double(6)` on the final line.

```{r function_definition, exercise=TRUE, topic="function_definition"}

```

```{r function_definition-solution}
double <- function(x) x * 2
double(6)
```

```{r function_definition-check}
grade_this({
  if (!uses_call(.user_code, "function")) {
    fail("Define the function using `function(x)`.")
  }
  if (!uses_call(.user_code, "<-")) {
    fail("Assign the function to the name `double` using `<-`.")
  }
  if (!identical(.result, 12)) {
    fail("Your final expression should be `double(6)`, which returns 12.")
  }
  pass("Correct: you defined and called an R function.")
})
```

## Drill 8: Logical subsetting

The vector `scores` is provided. Using `[ ]` and a logical comparison, return only the values greater than or equal to 80.

```{r logical_subset-setup, include=FALSE}
scores <- c(74, 91, 80, 67, 88)
```

```{r logical_subset, exercise=TRUE, exercise.setup="logical_subset-setup", topic="vector_indexing"}

```

```{r logical_subset-solution}
scores[scores >= 80]
```

```{r logical_subset-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use `[ ]` for logical subsetting.")
  }
  if (!uses_call(.user_code, ">=")) {
    fail("Use a `>=` comparison to create the logical index.")
  }
  if (!identical(.result, scores[scores >= 80])) {
    fail("Return only scores greater than or equal to 80.")
  }
  pass("Correct: you used a logical expression inside `[ ]`.")
})
```

## Finished

When each exercise displays a green **Correct** result, your successful attempt has been recorded. If the logging banner at the top ever turns red, correct the connection problem and resubmit the affected exercise.
