# Recursive expression-decomposition drill bank

These drills train students to read R as a tree of function/operator calls and arguments rather than as an undifferentiated line of text.

**Before these chunks**, source the helper once in the tutorial setup:

```r
source("R/expression_decomposition.R")
```

Each drill:

1. shows one R expression;
2. asks for the outermost function/operator;
3. asks how many arguments it has;
4. asks for each argument exactly as an R expression;
5. asks whether each argument is another call, an atom, or a deliberately missing argument;
6. recursively repeats the process for every nested call;
7. classifies terminal atoms as symbols, numeric/integer/character/logical/complex literals, or `NULL`.

Operators such as `$`, `[`, `:`, `==`, `&`, `+`, `<-`, and unary `!`/`-` are intentionally treated as calls too.

## Expression Drill D01: Single function call

Take this expression completely apart:

```r
mean(x)
```

```{r expr_d01, echo=FALSE}
expression_decomposition_quiz(
  "mean(x)",
  caption = "Expression Drill D01"
)
```

## Expression Drill D02: Function with two arguments

Take this expression completely apart:

```r
round(3.14159, 2)
```

```{r expr_d02, echo=FALSE}
expression_decomposition_quiz(
  "round(3.14159, 2)",
  caption = "Expression Drill D02"
)
```

## Expression Drill D03: Vector construction

Take this expression completely apart:

```r
c(4, 7, 9)
```

```{r expr_d03, echo=FALSE}
expression_decomposition_quiz(
  "c(4, 7, 9)",
  caption = "Expression Drill D03"
)
```

## Expression Drill D04: Colon operator

Take this expression completely apart:

```r
1:10
```

```{r expr_d04, echo=FALSE}
expression_decomposition_quiz(
  "1:10",
  caption = "Expression Drill D04"
)
```

## Expression Drill D05: Dollar extraction

Take this expression completely apart:

```r
mtcars$mpg
```

```{r expr_d05, echo=FALSE}
expression_decomposition_quiz(
  "mtcars$mpg",
  caption = "Expression Drill D05"
)
```

## Expression Drill D06: Simple vector subscript

Take this expression completely apart:

```r
x[3]
```

```{r expr_d06, echo=FALSE}
expression_decomposition_quiz(
  "x[3]",
  caption = "Expression Drill D06"
)
```

## Expression Drill D07: Subscript built by c()

Take this expression completely apart:

```r
x[c(1, 4, 6)]
```

```{r expr_d07, echo=FALSE}
expression_decomposition_quiz(
  "x[c(1, 4, 6)]",
  caption = "Expression Drill D07"
)
```

## Expression Drill D08: Comparison operator

Take this expression completely apart:

```r
x > 5
```

```{r expr_d08, echo=FALSE}
expression_decomposition_quiz(
  "x > 5",
  caption = "Expression Drill D08"
)
```

## Expression Drill D09: Nested arithmetic

Take this expression completely apart:

```r
sqrt(16) + 2
```

```{r expr_d09, echo=FALSE}
expression_decomposition_quiz(
  "sqrt(16) + 2",
  caption = "Expression Drill D09"
)
```

## Expression Drill D10: Two-dimensional subsetting

Take this expression completely apart:

```r
iris[1:5, 1:2]
```

```{r expr_d10, echo=FALSE}
expression_decomposition_quiz(
  "iris[1:5, 1:2]",
  caption = "Expression Drill D10"
)
```

## Expression Drill D11: Function around dollar extraction

Take this expression completely apart:

```r
mean(mtcars$mpg)
```

```{r expr_d11, echo=FALSE}
expression_decomposition_quiz(
  "mean(mtcars$mpg)",
  caption = "Expression Drill D11"
)
```

## Expression Drill D12: Function around comparison

Take this expression completely apart:

```r
sum(mtcars$cyl == 4)
```

```{r expr_d12, echo=FALSE}
expression_decomposition_quiz(
  "sum(mtcars$cyl == 4)",
  caption = "Expression Drill D12"
)
```

## Expression Drill D13: Two nested functions

Take this expression completely apart:

```r
round(mean(mtcars$mpg), 1)
```

```{r expr_d13, echo=FALSE}
expression_decomposition_quiz(
  "round(mean(mtcars$mpg), 1)",
  caption = "Expression Drill D13"
)
```

## Expression Drill D14: Subsetting with a missing column argument

Take this expression completely apart:

```r
iris[iris$Species == "setosa", ]
```

```{r expr_d14, echo=FALSE}
expression_decomposition_quiz(
  "iris[iris$Species == \"setosa\", ]",
  caption = "Expression Drill D14"
)
```

## Expression Drill D15: Row condition plus selected columns

Take this expression completely apart:

```r
mtcars[mtcars$cyl == 4, c("mpg", "hp")]
```

```{r expr_d15, echo=FALSE}
expression_decomposition_quiz(
  "mtcars[mtcars$cyl == 4, c(\"mpg\", \"hp\")]",
  caption = "Expression Drill D15"
)
```

## Expression Drill D16: Vector selected by its own values

Take this expression completely apart:

```r
x[x > 0]
```

```{r expr_d16, echo=FALSE}
expression_decomposition_quiz(
  "x[x > 0]",
  caption = "Expression Drill D16"
)
```

## Expression Drill D17: Function around logical subsetting

Take this expression completely apart:

```r
mean(x[x > 0])
```

```{r expr_d17, echo=FALSE}
expression_decomposition_quiz(
  "mean(x[x > 0])",
  caption = "Expression Drill D17"
)
```

## Expression Drill D18: Named function argument

Take this expression completely apart:

```r
paste(first, last, sep = " ")
```

```{r expr_d18, echo=FALSE}
expression_decomposition_quiz(
  "paste(first, last, sep = \" \")",
  caption = "Expression Drill D18"
)
```

## Expression Drill D19: Two nested colon calls

Take this expression completely apart:

```r
c(1:3, 8:10)
```

```{r expr_d19, echo=FALSE}
expression_decomposition_quiz(
  "c(1:3, 8:10)",
  caption = "Expression Drill D19"
)
```

## Expression Drill D20: Three-argument conditional

Take this expression completely apart:

```r
ifelse(x > 0, x, 0)
```

```{r expr_d20, echo=FALSE}
expression_decomposition_quiz(
  "ifelse(x > 0, x, 0)",
  caption = "Expression Drill D20"
)
```

## Expression Drill D21: Mean of conditionally selected column

Take this expression completely apart:

```r
mean(mtcars$mpg[mtcars$cyl == 4])
```

```{r expr_d21, echo=FALSE}
expression_decomposition_quiz(
  "mean(mtcars$mpg[mtcars$cyl == 4])",
  caption = "Expression Drill D21"
)
```

## Expression Drill D22: Missing-value filter inside mean

Take this expression completely apart:

```r
round(mean(airquality$Ozone[!is.na(airquality$Ozone)]), 1)
```

```{r expr_d22, echo=FALSE}
expression_decomposition_quiz(
  "round(mean(airquality$Ozone[!is.na(airquality$Ozone)]), 1)",
  caption = "Expression Drill D22"
)
```

## Expression Drill D23: Nested summary inside comparison

Take this expression completely apart:

```r
sum(iris$Sepal.Length > mean(iris$Sepal.Length))
```

```{r expr_d23, echo=FALSE}
expression_decomposition_quiz(
  "sum(iris$Sepal.Length > mean(iris$Sepal.Length))",
  caption = "Expression Drill D23"
)
```

## Expression Drill D24: Compound row condition

Take this expression completely apart:

```r
mtcars[mtcars$cyl == 4 & mtcars$mpg > 25, c("mpg", "hp", "wt")]
```

```{r expr_d24, echo=FALSE}
expression_decomposition_quiz(
  "mtcars[mtcars$cyl == 4 & mtcars$mpg > 25, c(\"mpg\", \"hp\", \"wt\")]",
  caption = "Expression Drill D24"
)
```

## Expression Drill D25: subset() with named select argument

Take this expression completely apart:

```r
subset(ToothGrowth, supp == "OJ" & dose == 2, select = c(len, dose))
```

```{r expr_d25, echo=FALSE}
expression_decomposition_quiz(
  "subset(ToothGrowth, supp == \"OJ\" & dose == 2, select = c(len, dose))",
  caption = "Expression Drill D25"
)
```

## Expression Drill D26: Names, subsetting, and paste

Take this expression completely apart:

```r
paste(names(x)[x > 0], collapse = ", ")
```

```{r expr_d26, echo=FALSE}
expression_decomposition_quiz(
  "paste(names(x)[x > 0], collapse = \", \")",
  caption = "Expression Drill D26"
)
```

## Expression Drill D27: Successive subscripts

Take this expression completely apart:

```r
x[c(TRUE, FALSE)][1:3]
```

```{r expr_d27, echo=FALSE}
expression_decomposition_quiz(
  "x[c(TRUE, FALSE)][1:3]",
  caption = "Expression Drill D27"
)
```

## Expression Drill D28: Arithmetic expression tree

Take this expression completely apart:

```r
round(sqrt(sum(x^2)), 2)
```

```{r expr_d28, echo=FALSE}
expression_decomposition_quiz(
  "round(sqrt(sum(x^2)), 2)",
  caption = "Expression Drill D28"
)
```

## Expression Drill D29: Combined vectors inside mean

Take this expression completely apart:

```r
mean(c(x[1:3], y[4:6]), na.rm = TRUE)
```

```{r expr_d29, echo=FALSE}
expression_decomposition_quiz(
  "mean(c(x[1:3], y[4:6]), na.rm = TRUE)",
  caption = "Expression Drill D29"
)
```

## Expression Drill D30: order() with named argument

Take this expression completely apart:

```r
order(mtcars$mpg, decreasing = TRUE)
```

```{r expr_d30, echo=FALSE}
expression_decomposition_quiz(
  "order(mtcars$mpg, decreasing = TRUE)",
  caption = "Expression Drill D30"
)
```

## Expression Drill D31: Ordered data-frame rows

Take this expression completely apart:

```r
mtcars[order(mtcars$mpg, decreasing = TRUE), c("mpg", "cyl", "wt")]
```

```{r expr_d31, echo=FALSE}
expression_decomposition_quiz(
  "mtcars[order(mtcars$mpg, decreasing = TRUE), c(\"mpg\", \"cyl\", \"wt\")]",
  caption = "Expression Drill D31"
)
```

## Expression Drill D32: Membership and comparison inside subsetting

Take this expression completely apart:

```r
mean(mtcars$mpg[mtcars$cyl %in% c(4, 6) & mtcars$wt < 3])
```

```{r expr_d32, echo=FALSE}
expression_decomposition_quiz(
  "mean(mtcars$mpg[mtcars$cyl %in% c(4, 6) & mtcars$wt < 3])",
  caption = "Expression Drill D32"
)
```

## Expression Drill D33: Variance-like arithmetic

Take this expression completely apart:

```r
round(sum((x - mean(x))^2) / (length(x) - 1), 2)
```

```{r expr_d33, echo=FALSE}
expression_decomposition_quiz(
  "round(sum((x - mean(x))^2) / (length(x) - 1), 2)",
  caption = "Expression Drill D33"
)
```

## Expression Drill D34: which(), names(), and paste

Take this expression completely apart:

```r
paste(names(which(x > mean(x))), collapse = ", ")
```

```{r expr_d34, echo=FALSE}
expression_decomposition_quiz(
  "paste(names(which(x > mean(x))), collapse = \", \")",
  caption = "Expression Drill D34"
)
```

## Expression Drill D35: Nested group-specific mean

Take this expression completely apart:

```r
iris[iris$Sepal.Length > mean(iris$Sepal.Length[iris$Species == "setosa"]), c("Sepal.Length", "Species")]
```

```{r expr_d35, echo=FALSE}
expression_decomposition_quiz(
  "iris[iris$Sepal.Length > mean(iris$Sepal.Length[iris$Species == \"setosa\"]), c(\"Sepal.Length\", \"Species\")]",
  caption = "Expression Drill D35"
)
```

## Expression Drill D36: ifelse() with missing-value replacement

Take this expression completely apart:

```r
ifelse(is.na(x), mean(x[!is.na(x)]), x)
```

```{r expr_d36, echo=FALSE}
expression_decomposition_quiz(
  "ifelse(is.na(x), mean(x[!is.na(x)]), x)",
  caption = "Expression Drill D36"
)
```

## Expression Drill D37: Two summaries inside a compound condition

Take this expression completely apart:

```r
sum(mtcars$mpg > mean(mtcars$mpg) & mtcars$hp < median(mtcars$hp))
```

```{r expr_d37, echo=FALSE}
expression_decomposition_quiz(
  "sum(mtcars$mpg > mean(mtcars$mpg) & mtcars$hp < median(mtcars$hp))",
  caption = "Expression Drill D37"
)
```

## Expression Drill D38: Membership filter plus named digits argument

Take this expression completely apart:

```r
round(mean(airquality$Temp[airquality$Month %in% c(6, 7, 8)]), digits = 1)
```

```{r expr_d38, echo=FALSE}
expression_decomposition_quiz(
  "round(mean(airquality$Temp[airquality$Month %in% c(6, 7, 8)]), digits = 1)",
  caption = "Expression Drill D38"
)
```

## Expression Drill D39: Three nested functions and a named argument

Take this expression completely apart:

```r
paste(sort(unique(iris$Species)), collapse = " / ")
```

```{r expr_d39, echo=FALSE}
expression_decomposition_quiz(
  "paste(sort(unique(iris$Species)), collapse = \" / \")",
  caption = "Expression Drill D39"
)
```

## Expression Drill D40: Quantile inside a row filter

Take this expression completely apart:

```r
mtcars[mtcars$mpg > quantile(mtcars$mpg, 0.75), c("mpg", "hp", "wt")]
```

```{r expr_d40, echo=FALSE}
expression_decomposition_quiz(
  "mtcars[mtcars$mpg > quantile(mtcars$mpg, 0.75), c(\"mpg\", \"hp\", \"wt\")]",
  caption = "Expression Drill D40"
)
```

## Expression Drill D41: Nested subgroup median

Take this expression completely apart:

```r
round(mean(mtcars$mpg[mtcars$cyl == 4 & mtcars$wt < median(mtcars$wt[mtcars$cyl == 4])]), 2)
```

```{r expr_d41, echo=FALSE}
expression_decomposition_quiz(
  "round(mean(mtcars$mpg[mtcars$cyl == 4 & mtcars$wt < median(mtcars$wt[mtcars$cyl == 4])]), 2)",
  caption = "Expression Drill D41"
)
```

## Expression Drill D42: Ordering by two expressions

Take this expression completely apart:

```r
iris[order(iris$Species, -iris$Sepal.Length), c("Species", "Sepal.Length", "Petal.Length")]
```

```{r expr_d42, echo=FALSE}
expression_decomposition_quiz(
  "iris[order(iris$Species, -iris$Sepal.Length), c(\"Species\", \"Sepal.Length\", \"Petal.Length\")]",
  caption = "Expression Drill D42"
)
```

## Expression Drill D43: Missingness and mean in one logical expression

Take this expression completely apart:

```r
sum(!is.na(airquality$Ozone) & airquality$Ozone > mean(airquality$Ozone, na.rm = TRUE))
```

```{r expr_d43, echo=FALSE}
expression_decomposition_quiz(
  "sum(!is.na(airquality$Ozone) & airquality$Ozone > mean(airquality$Ozone, na.rm = TRUE))",
  caption = "Expression Drill D43"
)
```

## Expression Drill D44: table(), sort(), names(), paste

Take this expression completely apart:

```r
paste(names(sort(table(mtcars$cyl), decreasing = TRUE)), collapse = ",")
```

```{r expr_d44, echo=FALSE}
expression_decomposition_quiz(
  "paste(names(sort(table(mtcars$cyl), decreasing = TRUE)), collapse = \",\")",
  caption = "Expression Drill D44"
)
```

## Expression Drill D45: Nested filtering and arithmetic

Take this expression completely apart:

```r
round(sqrt(sum((x[!is.na(x)] - mean(x, na.rm = TRUE))^2)), 3)
```

```{r expr_d45, echo=FALSE}
expression_decomposition_quiz(
  "round(sqrt(sum((x[!is.na(x)] - mean(x, na.rm = TRUE))^2)), 3)",
  caption = "Expression Drill D45"
)
```

## Expression Drill D46: Assignment as a function call

Take this expression completely apart:

```r
high_mpg <- mtcars[mtcars$mpg > mean(mtcars$mpg), c("mpg", "cyl", "wt")]
```

```{r expr_d46, echo=FALSE}
expression_decomposition_quiz(
  "high_mpg <- mtcars[mtcars$mpg > mean(mtcars$mpg), c(\"mpg\", \"cyl\", \"wt\")]",
  caption = "Expression Drill D46"
)
```

## Expression Drill D47: Assignment with two quantiles

Take this expression completely apart:

```r
result <- round(mean(x[x >= quantile(x, 0.25) & x <= quantile(x, 0.75)]), 2)
```

```{r expr_d47, echo=FALSE}
expression_decomposition_quiz(
  "result <- round(mean(x[x >= quantile(x, 0.25) & x <= quantile(x, 0.75)]), 2)",
  caption = "Expression Drill D47"
)
```

## Expression Drill D48: Row names selected by a summary comparison

Take this expression completely apart:

```r
paste(rownames(USArrests)[USArrests$Murder > mean(USArrests$Murder)], collapse = ", ")
```

```{r expr_d48, echo=FALSE}
expression_decomposition_quiz(
  "paste(rownames(USArrests)[USArrests$Murder > mean(USArrests$Murder)], collapse = \", \")",
  caption = "Expression Drill D48"
)
```

## Expression Drill D49: Names followed by vector subsetting

Take this expression completely apart:

```r
names(mtcars)[c(1, 3, 5)]
```

```{r expr_d49, echo=FALSE}
expression_decomposition_quiz(
  "names(mtcars)[c(1, 3, 5)]",
  caption = "Expression Drill D49"
)
```

## Expression Drill D50: Row names with nested mean filter

Take this expression completely apart:

```r
rownames(mtcars)[mtcars$mpg > mean(mtcars$mpg)]
```

```{r expr_d50, echo=FALSE}
expression_decomposition_quiz(
  "rownames(mtcars)[mtcars$mpg > mean(mtcars$mpg)]",
  caption = "Expression Drill D50"
)
```

