<!-- question: vector_c08a -->
## Vector Drill C08a: Named numeric vector

Using `c()`, create a vector with these entries in order: `north = 12.5, south = 9, west = 14.25`. Assign it to `region_rates`, then put `region_rates` on the final line.

```{r vector_c08a, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c08a-solution}
region_rates <- c(north = 12.5, south = 9, west = 14.25)
region_rates
```

```{r vector_c08a-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "region_rates",
    expected_value = c(north = 12.5, south = 9, west = 14.25),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c08b -->
## Vector Drill C08b: Named numeric vector

Using `c()`, create a vector with these entries in order: `pre = 118, post = 110, final = 106`. Assign it to `BP`, then put `BP` on the final line.

```{r vector_c08b, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c08b-solution}
BP <- c(pre = 118, post = 110, final = 106)
BP
```

```{r vector_c08b-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "BP",
    expected_value = c(pre = 118, post = 110, final = 106),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c08c -->
## Vector Drill C08c: Named numeric vector

Using `c()`, create a vector with these entries in order: `glucose = 93, sodium = 140, potassium = 4.2`. Assign it to `lab.values`, then put `lab.values` on the final line.

```{r vector_c08c, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c08c-solution}
lab.values <- c(glucose = 93, sodium = 140, potassium = 4.2)
lab.values
```

```{r vector_c08c-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "lab.values",
    expected_value = c(glucose = 93, sodium = 140, potassium = 4.2),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c08d -->
## Vector Drill C08d: Named numeric vector

Using `c()`, create a vector with these entries in order: `math = 88, reading = 94, science = 91`. Assign it to `SCORES`, then put `SCORES` on the final line.

```{r vector_c08d, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c08d-solution}
SCORES <- c(math = 88, reading = 94, science = 91)
SCORES
```

```{r vector_c08d-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "SCORES",
    expected_value = c(math = 88, reading = 94, science = 91),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c09a -->
## Vector Drill C09a: Named character vector

Using `c()`, create a vector with these entries in order: `lead = "Ada", backup = "Grace", reviewer = "Rita"`. Assign it to `staff`, then put `staff` on the final line.

```{r vector_c09a, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c09a-solution}
staff <- c(lead = "Ada", backup = "Grace", reviewer = "Rita")
staff
```

```{r vector_c09a-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "staff",
    expected_value = c(lead = "Ada", backup = "Grace", reviewer = "Rita"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c09b -->
## Vector Drill C09b: Named character vector

Using `c()`, create a vector with these entries in order: `primary = "srv01", backup = "srv02", archive = "srv09"`. Assign it to `SERVER_MAP`, then put `SERVER_MAP` on the final line.

```{r vector_c09b, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c09b-solution}
SERVER_MAP <- c(primary = "srv01", backup = "srv02", archive = "srv09")
SERVER_MAP
```

```{r vector_c09b-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "SERVER_MAP",
    expected_value = c(primary = "srv01", backup = "srv02", archive = "srv09"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c09c -->
## Vector Drill C09c: Named character vector

Using `c()`, create a vector with these entries in order: `north = "Alpha", central = "Bravo", south = "Charlie"`. Assign it to `site.names`, then put `site.names` on the final line.

```{r vector_c09c, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c09c-solution}
site.names <- c(north = "Alpha", central = "Bravo", south = "Charlie")
site.names
```

```{r vector_c09c-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "site.names",
    expected_value = c(north = "Alpha", central = "Bravo", south = "Charlie"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c09d -->
## Vector Drill C09d: Named character vector

Using `c()`, create a vector with these entries in order: `first = "RXA", second = "RXB", third = "RXC"`. Assign it to `rx_codes`, then put `rx_codes` on the final line.

```{r vector_c09d, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c09d-solution}
rx_codes <- c(first = "RXA", second = "RXB", third = "RXC")
rx_codes
```

```{r vector_c09d-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "rx_codes",
    expected_value = c(first = "RXA", second = "RXB", third = "RXC"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c10a -->
## Vector Drill C10a: Named logical vector

Using `c()`, create a vector with these entries in order: `ready = TRUE, late = FALSE, reviewed = TRUE`. Assign it to `workflow`, then put `workflow` on the final line.

```{r vector_c10a, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c10a-solution}
workflow <- c(ready = TRUE, late = FALSE, reviewed = TRUE)
workflow
```

```{r vector_c10a-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "workflow",
    expected_value = c(ready = TRUE, late = FALSE, reviewed = TRUE),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c10b -->
## Vector Drill C10b: Named logical vector

Using `c()`, create a vector with these entries in order: `passed = TRUE, flagged = FALSE, repeated = FALSE`. Assign it to `QC_STATUS`, then put `QC_STATUS` on the final line.

```{r vector_c10b, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c10b-solution}
QC_STATUS <- c(passed = TRUE, flagged = FALSE, repeated = FALSE)
QC_STATUS
```

```{r vector_c10b-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "QC_STATUS",
    expected_value = c(passed = TRUE, flagged = FALSE, repeated = FALSE),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c10c -->
## Vector Drill C10c: Named logical vector

Using `c()`, create a vector with these entries in order: `eligible = TRUE, enrolled = TRUE, complete = FALSE`. Assign it to `visit.flags`, then put `visit.flags` on the final line.

```{r vector_c10c, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c10c-solution}
visit.flags <- c(eligible = TRUE, enrolled = TRUE, complete = FALSE)
visit.flags
```

```{r vector_c10c-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "visit.flags",
    expected_value = c(eligible = TRUE, enrolled = TRUE, complete = FALSE),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c10d -->
## Vector Drill C10d: Named logical vector

Using `c()`, create a vector with these entries in order: `high = FALSE, medium = TRUE, low = TRUE`. Assign it to `alerts`, then put `alerts` on the final line.

```{r vector_c10d, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c10d-solution}
alerts <- c(high = FALSE, medium = TRUE, low = TRUE)
alerts
```

```{r vector_c10d-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "alerts",
    expected_value = c(high = FALSE, medium = TRUE, low = TRUE),
    required_calls = c("c")
  )
})
```
<!-- /question -->
