<!-- question: vector_c01a -->
## Vector Drill C01a: Explicit numeric vector

Using `c()`, create a vector with these entries in order: `2, 5, 9, 14`. Assign it to `scores`, then put `scores` on the final line.

```{r vector_c01a, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c01a-solution}
scores <- c(2, 5, 9, 14)
scores
```

```{r vector_c01a-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "scores",
    expected_value = c(2, 5, 9, 14),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c01b -->
## Vector Drill C01b: Explicit numeric vector

Using `c()`, create a vector with these entries in order: `1.5, 3, 8.25, 11`. Assign it to `dose_values`, then put `dose_values` on the final line.

```{r vector_c01b, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c01b-solution}
dose_values <- c(1.5, 3, 8.25, 11)
dose_values
```

```{r vector_c01b-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "dose_values",
    expected_value = c(1.5, 3, 8.25, 11),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c01c -->
## Vector Drill C01c: Explicit numeric vector

Using `c()`, create a vector with these entries in order: `-3, 0, 6, 12`. Assign it to `LAB`, then put `LAB` on the final line.

```{r vector_c01c, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c01c-solution}
LAB <- c(-3, 0, 6, 12)
LAB
```

```{r vector_c01c-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "LAB",
    expected_value = c(-3, 0, 6, 12),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c01d -->
## Vector Drill C01d: Explicit numeric vector

Using `c()`, create a vector with these entries in order: `4, 7, 7, 13`. Assign it to `visit.counts`, then put `visit.counts` on the final line.

```{r vector_c01d, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c01d-solution}
visit.counts <- c(4, 7, 7, 13)
visit.counts
```

```{r vector_c01d-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "visit.counts",
    expected_value = c(4, 7, 7, 13),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c02a -->
## Vector Drill C02a: Explicit character vector

Using `c()`, create a vector with these entries in order: `"red", "green", "blue"`. Assign it to `colors`, then put `colors` on the final line.

```{r vector_c02a, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c02a-solution}
colors <- c("red", "green", "blue")
colors
```

```{r vector_c02a-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "colors",
    expected_value = c("red", "green", "blue"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c02b -->
## Vector Drill C02b: Explicit character vector

Using `c()`, create a vector with these entries in order: `"NE", "SW", "MW", "SE"`. Assign it to `site_codes`, then put `site_codes` on the final line.

```{r vector_c02b, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c02b-solution}
site_codes <- c("NE", "SW", "MW", "SE")
site_codes
```

```{r vector_c02b-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "site_codes",
    expected_value = c("NE", "SW", "MW", "SE"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c02c -->
## Vector Drill C02c: Explicit character vector

Using `c()`, create a vector with these entries in order: `"new", "open", "closed"`. Assign it to `STATUS`, then put `STATUS` on the final line.

```{r vector_c02c, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c02c-solution}
STATUS <- c("new", "open", "closed")
STATUS
```

```{r vector_c02c-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "STATUS",
    expected_value = c("new", "open", "closed"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c02d -->
## Vector Drill C02d: Explicit character vector

Using `c()`, create a vector with these entries in order: `"cbc", "cmp", "a1c", "tsh"`. Assign it to `lab.labels`, then put `lab.labels` on the final line.

```{r vector_c02d, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c02d-solution}
lab.labels <- c("cbc", "cmp", "a1c", "tsh")
lab.labels
```

```{r vector_c02d-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "lab.labels",
    expected_value = c("cbc", "cmp", "a1c", "tsh"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c03a -->
## Vector Drill C03a: Explicit logical vector

Using `c()`, create a vector with these entries in order: `TRUE, FALSE, FALSE, TRUE`. Assign it to `flags`, then put `flags` on the final line.

```{r vector_c03a, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c03a-solution}
flags <- c(TRUE, FALSE, FALSE, TRUE)
flags
```

```{r vector_c03a-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "flags",
    expected_value = c(TRUE, FALSE, FALSE, TRUE),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c03b -->
## Vector Drill C03b: Explicit logical vector

Using `c()`, create a vector with these entries in order: `FALSE, TRUE, TRUE, FALSE, TRUE`. Assign it to `QC_flags`, then put `QC_flags` on the final line.

```{r vector_c03b, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c03b-solution}
QC_flags <- c(FALSE, TRUE, TRUE, FALSE, TRUE)
QC_flags
```

```{r vector_c03b-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "QC_flags",
    expected_value = c(FALSE, TRUE, TRUE, FALSE, TRUE),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c03c -->
## Vector Drill C03c: Explicit logical vector

Using `c()`, create a vector with these entries in order: `TRUE, TRUE, FALSE`. Assign it to `ACTIVE`, then put `ACTIVE` on the final line.

```{r vector_c03c, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c03c-solution}
ACTIVE <- c(TRUE, TRUE, FALSE)
ACTIVE
```

```{r vector_c03c-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "ACTIVE",
    expected_value = c(TRUE, TRUE, FALSE),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c03d -->
## Vector Drill C03d: Explicit logical vector

Using `c()`, create a vector with these entries in order: `FALSE, FALSE, TRUE, TRUE`. Assign it to `review.done`, then put `review.done` on the final line.

```{r vector_c03d, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c03d-solution}
review.done <- c(FALSE, FALSE, TRUE, TRUE)
review.done
```

```{r vector_c03d-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "review.done",
    expected_value = c(FALSE, FALSE, TRUE, TRUE),
    required_calls = c("c")
  )
})
```
<!-- /question -->
