<!-- question: vector_c11a -->
## Vector Drill C11a: Vector containing `NA`

Using `c()`, create a vector with these entries in order: `2.5, NA, 7.5, 9`. Assign it to `measurements`, then put `measurements` on the final line.

```{r vector_c11a, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c11a-solution}
measurements <- c(2.5, NA, 7.5, 9)
measurements
```

```{r vector_c11a-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "measurements",
    expected_value = c(2.5, NA, 7.5, 9),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c11b -->
## Vector Drill C11b: Vector containing `NA`

Using `c()`, create a vector with these entries in order: `"alpha", NA, "omega", "final"`. Assign it to `codes`, then put `codes` on the final line.

```{r vector_c11b, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c11b-solution}
codes <- c("alpha", NA, "omega", "final")
codes
```

```{r vector_c11b-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "codes",
    expected_value = c("alpha", NA, "omega", "final"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c11c -->
## Vector Drill C11c: Vector containing `NA`

Using `c()`, create a vector with these entries in order: `TRUE, NA, FALSE, TRUE`. Assign it to `FLAGS`, then put `FLAGS` on the final line.

```{r vector_c11c, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c11c-solution}
FLAGS <- c(TRUE, NA, FALSE, TRUE)
FLAGS
```

```{r vector_c11c-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "FLAGS",
    expected_value = c(TRUE, NA, FALSE, TRUE),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c11d -->
## Vector Drill C11d: Vector containing `NA`

Using `c()`, create a vector with these entries in order: `14, 18, NA, 21, 24`. Assign it to `visit_values`, then put `visit_values` on the final line.

```{r vector_c11d, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c11d-solution}
visit_values <- c(14, 18, NA, 21, 24)
visit_values
```

```{r vector_c11d-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "visit_values",
    expected_value = c(14, 18, NA, 21, 24),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c12a -->
## Vector Drill C12a: Named vector containing `NA`

Using `c()`, create a vector with these entries in order: `baseline = 8.2, month3 = NA, final = 7.1`. Assign it to `followup`, then put `followup` on the final line.

```{r vector_c12a, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c12a-solution}
followup <- c(baseline = 8.2, month3 = NA, final = 7.1)
followup
```

```{r vector_c12a-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "followup",
    expected_value = c(baseline = 8.2, month3 = NA, final = 7.1),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c12b -->
## Vector Drill C12b: Named vector containing `NA`

Using `c()`, create a vector with these entries in order: `cbc = "done", cmp = NA, a1c = "pending"`. Assign it to `LAB_STATUS`, then put `LAB_STATUS` on the final line.

```{r vector_c12b, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c12b-solution}
LAB_STATUS <- c(cbc = "done", cmp = NA, a1c = "pending")
LAB_STATUS
```

```{r vector_c12b-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "LAB_STATUS",
    expected_value = c(cbc = "done", cmp = NA, a1c = "pending"),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c12c -->
## Vector Drill C12c: Named vector containing `NA`

Using `c()`, create a vector with these entries in order: `initial = TRUE, second = NA, final = FALSE`. Assign it to `review.flags`, then put `review.flags` on the final line.

```{r vector_c12c, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c12c-solution}
review.flags <- c(initial = TRUE, second = NA, final = FALSE)
review.flags
```

```{r vector_c12c-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "review.flags",
    expected_value = c(initial = TRUE, second = NA, final = FALSE),
    required_calls = c("c")
  )
})
```
<!-- /question -->

<!-- question: vector_c12d -->
## Vector Drill C12d: Named vector containing `NA`

Using `c()`, create a vector with these entries in order: `low = 2.5, medium = NA, high = 7.5`. Assign it to `dose.values`, then put `dose.values` on the final line.

```{r vector_c12d, exercise=TRUE, topic="vector_creation"}

```

```{r vector_c12d-solution}
dose.values <- c(low = 2.5, medium = NA, high = 7.5)
dose.values
```

```{r vector_c12d-check}
grade_this({
  check_vector_assignment(
    code = .user_code,
    result_env = .envir_result,
    variable_name = "dose.values",
    expected_value = c(low = 2.5, medium = NA, high = 7.5),
    required_calls = c("c")
  )
})
```
<!-- /question -->
