<!-- question: vector_e13a -->
## Vector Drill E13a: Use `which()` inside brackets

The vector `measurements` is provided. `which()` takes a logical vector and returns the positions where it is `TRUE`. Use `which()` inside `[ ]` to return values greater than 8. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e13a-setup, include=FALSE}
measurements <- c(4, 9, 12, 3, 18, 7)
```

```{r vector_e13a, exercise=TRUE, exercise.setup="vector_e13a-setup", topic="vector_indexing"}

```

```{r vector_e13a-solution}
measurements[which(measurements > 8)]
```

```{r vector_e13a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("which"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e13b -->
## Vector Drill E13b: Use `which()` inside brackets

The vector `SCORES` is provided. `which()` returns the positions where a logical condition is `TRUE`. Use it inside `[ ]` to return scores at least 80. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e13b-setup, include=FALSE}
SCORES <- c(55, 72, 88, 61, 95, 79)
```

```{r vector_e13b, exercise=TRUE, exercise.setup="vector_e13b-setup", topic="vector_indexing"}

```

```{r vector_e13b-solution}
SCORES[which(SCORES >= 80)]
```

```{r vector_e13b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("which"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e13c -->
## Vector Drill E13c: Use `which()` inside brackets

The vector `lab.values` is provided. `which()` returns positions where its logical input is `TRUE`. Use it inside `[ ]` to return values below 3. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e13c-setup, include=FALSE}
lab.values <- c(1.2, 5.1, 2.8, 7.4, 3.3, 9.2)
```

```{r vector_e13c, exercise=TRUE, exercise.setup="vector_e13c-setup", topic="vector_indexing"}

```

```{r vector_e13c-solution}
lab.values[which(lab.values < 3)]
```

```{r vector_e13c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("which"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e13d -->
## Vector Drill E13d: Use `which()` inside brackets

The vector `visit_days` is provided. `which()` returns positions where a logical condition is `TRUE`. Use it inside `[ ]` to return visit days from 10 through 30 inclusive. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e13d-setup, include=FALSE}
visit_days <- c(2, 5, 9, 14, 20, 27, 35)
```

```{r vector_e13d, exercise=TRUE, exercise.setup="vector_e13d-setup", topic="vector_indexing"}

```

```{r vector_e13d-solution}
visit_days[which(visit_days >= 10 & visit_days <= 30)]
```

```{r vector_e13d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("which"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e14a -->
## Vector Drill E14a: Use `grep()` inside brackets

The vector `codes` is provided. `grep(pattern, text)` returns the positions of character values matching `pattern`. Use `grep()` inside `[ ]` to return the codes containing `AX`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e14a-setup, include=FALSE}
codes <- c("AX1", "BY2", "AX3", "CZ4", "AX5")
```

```{r vector_e14a, exercise=TRUE, exercise.setup="vector_e14a-setup", topic="vector_indexing"}

```

```{r vector_e14a-solution}
codes[grep("AX", codes)]
```

```{r vector_e14a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("grep"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e14b -->
## Vector Drill E14b: Use `grep()` inside brackets

The vector `SITE_NAMES` is provided. `grep(pattern, text)` returns positions of matching strings. Use it inside `[ ]` to return entries containing `lab`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e14b-setup, include=FALSE}
SITE_NAMES <- c("north-clinic", "south-lab", "north-lab", "west-clinic")
```

```{r vector_e14b, exercise=TRUE, exercise.setup="vector_e14b-setup", topic="vector_indexing"}

```

```{r vector_e14b-solution}
SITE_NAMES[grep("lab", SITE_NAMES)]
```

```{r vector_e14b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("grep"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e14c -->
## Vector Drill E14c: Use `grep()` inside brackets

The vector `status.text` is provided. `grep(pattern, text)` returns positions of matching strings. Use it inside `[ ]` to return entries containing `review`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e14c-setup, include=FALSE}
status.text <- c("ready", "review", "held", "reviewed", "done")
```

```{r vector_e14c, exercise=TRUE, exercise.setup="vector_e14c-setup", topic="vector_indexing"}

```

```{r vector_e14c-solution}
status.text[grep("review", status.text)]
```

```{r vector_e14c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("grep"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e14d -->
## Vector Drill E14d: Use `grep()` inside brackets

The vector `rx_codes` is provided. `grep(pattern, text)` returns positions of matching strings. Use it inside `[ ]` to return entries containing `RXA`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e14d-setup, include=FALSE}
rx_codes <- c("RXA-10", "RQB-20", "RXA-30", "TXC-40", "RXA-50")
```

```{r vector_e14d, exercise=TRUE, exercise.setup="vector_e14d-setup", topic="vector_indexing"}

```

```{r vector_e14d-solution}
rx_codes[grep("RXA", rx_codes)]
```

```{r vector_e14d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("grep"),
    min_brackets = 1
  )
})
```
<!-- /question -->
