<!-- question: vector_e01a -->
## Vector Drill E01a: One element by position

The vector `measurements` is provided. Return the third element. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e01a-setup, include=FALSE}
measurements <- c(10, 20, 30, 40, 50)
```

```{r vector_e01a, exercise=TRUE, exercise.setup="vector_e01a-setup", topic="vector_indexing"}

```

```{r vector_e01a-solution}
measurements[3]
```

```{r vector_e01a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e01b -->
## Vector Drill E01b: One element by position

The vector `COLORS` is provided. Return the second element. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e01b-setup, include=FALSE}
COLORS <- c("red", "green", "blue", "black")
```

```{r vector_e01b, exercise=TRUE, exercise.setup="vector_e01b-setup", topic="vector_indexing"}

```

```{r vector_e01b-solution}
COLORS[2]
```

```{r vector_e01b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e01c -->
## Vector Drill E01c: One element by position

The vector `site.codes` is provided. Return the fifth element. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e01c-setup, include=FALSE}
site.codes <- c("AA", "BB", "CC", "DD", "EE", "FF")
```

```{r vector_e01c, exercise=TRUE, exercise.setup="vector_e01c-setup", topic="vector_indexing"}

```

```{r vector_e01c-solution}
site.codes[5]
```

```{r vector_e01c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e01d -->
## Vector Drill E01d: One element by position

The vector `visit_days` is provided. Return the sixth element. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e01d-setup, include=FALSE}
visit_days <- c(2, 5, 9, 14, 20, 27, 35)
```

```{r vector_e01d, exercise=TRUE, exercise.setup="vector_e01d-setup", topic="vector_indexing"}

```

```{r vector_e01d-solution}
visit_days[6]
```

```{r vector_e01d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e02a -->
## Vector Drill E02a: Several positions in a specified order

The vector `animals` is provided. Return the second and fifth elements, in that order. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e02a-setup, include=FALSE}
animals <- c("ant", "bee", "cat", "dog", "eel")
```

```{r vector_e02a, exercise=TRUE, exercise.setup="vector_e02a-setup", topic="vector_indexing"}

```

```{r vector_e02a-solution}
animals[c(2, 5)]
```

```{r vector_e02a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e02b -->
## Vector Drill E02b: Several positions in a specified order

The vector `SCORES` is provided. Return the sixth, first, and fourth elements, in that order. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e02b-setup, include=FALSE}
SCORES <- c(11, 22, 33, 44, 55, 66)
```

```{r vector_e02b, exercise=TRUE, exercise.setup="vector_e02b-setup", topic="vector_indexing"}

```

```{r vector_e02b-solution}
SCORES[c(6, 1, 4)]
```

```{r vector_e02b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e02c -->
## Vector Drill E02c: Several positions in a specified order

The vector `lab.values` is provided. Return the third, seventh, and second elements, in that order. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e02c-setup, include=FALSE}
lab.values <- c(3.1, 4.2, 5.3, 6.4, 7.5, 8.6, 9.7)
```

```{r vector_e02c, exercise=TRUE, exercise.setup="vector_e02c-setup", topic="vector_indexing"}

```

```{r vector_e02c-solution}
lab.values[c(3, 7, 2)]
```

```{r vector_e02c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e02d -->
## Vector Drill E02d: Several positions in a specified order

The vector `status_codes` is provided. Return the fourth, second, and first elements, in that order. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e02d-setup, include=FALSE}
status_codes <- c("new", "open", "held", "done", "void")
```

```{r vector_e02d, exercise=TRUE, exercise.setup="vector_e02d-setup", topic="vector_indexing"}

```

```{r vector_e02d-solution}
status_codes[c(4, 2, 1)]
```

```{r vector_e02d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e03a -->
## Vector Drill E03a: Contiguous subvector

The vector `values` is provided. Return elements 2 through 5. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e03a-setup, include=FALSE}
values <- c(5, 10, 15, 20, 25, 30)
```

```{r vector_e03a, exercise=TRUE, exercise.setup="vector_e03a-setup", topic="vector_indexing"}

```

```{r vector_e03a-solution}
values[2:5]
```

```{r vector_e03a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e03b -->
## Vector Drill E03b: Contiguous subvector

The vector `LETTERS2` is provided. Return elements 3 through 6. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e03b-setup, include=FALSE}
LETTERS2 <- c("aa", "bb", "cc", "dd", "ee", "ff", "gg")
```

```{r vector_e03b, exercise=TRUE, exercise.setup="vector_e03b-setup", topic="vector_indexing"}

```

```{r vector_e03b-solution}
LETTERS2[3:6]
```

```{r vector_e03b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e03c -->
## Vector Drill E03c: Contiguous subvector

The vector `visit.counts` is provided. Return elements 4 through 7. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e03c-setup, include=FALSE}
visit.counts <- c(1, 4, 7, 10, 13, 16, 19, 22)
```

```{r vector_e03c, exercise=TRUE, exercise.setup="vector_e03c-setup", topic="vector_indexing"}

```

```{r vector_e03c-solution}
visit.counts[4:7]
```

```{r vector_e03c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e03d -->
## Vector Drill E03d: Contiguous subvector

The vector `dose_levels` is provided. Return elements 5 through 8. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e03d-setup, include=FALSE}
dose_levels <- c(0.5, 1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5)
```

```{r vector_e03d, exercise=TRUE, exercise.setup="vector_e03d-setup", topic="vector_indexing"}

```

```{r vector_e03d-solution}
dose_levels[5:8]
```

```{r vector_e03d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e04a -->
## Vector Drill E04a: Reverse a contiguous section

The vector `codes` is provided. Return elements 6, 5, 4, and 3, in that order. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e04a-setup, include=FALSE}
codes <- c("aa", "bb", "cc", "dd", "ee", "ff", "gg")
```

```{r vector_e04a, exercise=TRUE, exercise.setup="vector_e04a-setup", topic="vector_indexing"}

```

```{r vector_e04a-solution}
codes[6:3]
```

```{r vector_e04a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e04b -->
## Vector Drill E04b: Reverse a contiguous section

The vector `VISITS` is provided. Return elements 7, 6, 5, and 4, in that order. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e04b-setup, include=FALSE}
VISITS <- c(10, 20, 30, 40, 50, 60, 70, 80)
```

```{r vector_e04b, exercise=TRUE, exercise.setup="vector_e04b-setup", topic="vector_indexing"}

```

```{r vector_e04b-solution}
VISITS[7:4]
```

```{r vector_e04b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e04c -->
## Vector Drill E04c: Reverse a contiguous section

The vector `lab.results` is provided. Return elements 5, 4, 3, and 2, in that order. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e04c-setup, include=FALSE}
lab.results <- c(2.1, 3.2, 4.3, 5.4, 6.5, 7.6)
```

```{r vector_e04c, exercise=TRUE, exercise.setup="vector_e04c-setup", topic="vector_indexing"}

```

```{r vector_e04c-solution}
lab.results[5:2]
```

```{r vector_e04c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e04d -->
## Vector Drill E04d: Reverse a contiguous section

The vector `day_names` is provided. Return elements 7, 6, 5, 4, and 3, in that order. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e04d-setup, include=FALSE}
day_names <- c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun")
```

```{r vector_e04d, exercise=TRUE, exercise.setup="vector_e04d-setup", topic="vector_indexing"}

```

```{r vector_e04d-solution}
day_names[7:3]
```

```{r vector_e04d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 1
  )
})
```
<!-- /question -->
