<!-- question: vector_e17a -->
## Vector Drill E17a: Use `startsWith()` inside brackets

The vector `codes` is provided. `startsWith(text, prefix)` returns a logical vector indicating which strings begin with `prefix`. Use it inside `[ ]` to return codes beginning with `AB`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e17a-setup, include=FALSE}
codes <- c("AB10", "CD20", "AB30", "EF40", "AB50")
```

```{r vector_e17a, exercise=TRUE, exercise.setup="vector_e17a-setup", topic="vector_indexing"}

```

```{r vector_e17a-solution}
codes[startsWith(codes, "AB")]
```

```{r vector_e17a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("startsWith"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e17b -->
## Vector Drill E17b: Use `startsWith()` inside brackets

The vector `SITE_NAMES` is provided. `startsWith(text, prefix)` returns a logical vector. Use it inside `[ ]` to return entries beginning with `north`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e17b-setup, include=FALSE}
SITE_NAMES <- c("north-clinic", "south-lab", "north-lab", "west-clinic")
```

```{r vector_e17b, exercise=TRUE, exercise.setup="vector_e17b-setup", topic="vector_indexing"}

```

```{r vector_e17b-solution}
SITE_NAMES[startsWith(SITE_NAMES, "north")]
```

```{r vector_e17b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("startsWith"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e17c -->
## Vector Drill E17c: Use `startsWith()` inside brackets

The vector `status.text` is provided. `startsWith(text, prefix)` returns a logical vector. Use it inside `[ ]` to return entries beginning with `pre`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e17c-setup, include=FALSE}
status.text <- c("precheck", "postcheck", "preview", "final", "prepare")
```

```{r vector_e17c, exercise=TRUE, exercise.setup="vector_e17c-setup", topic="vector_indexing"}

```

```{r vector_e17c-solution}
status.text[startsWith(status.text, "pre")]
```

```{r vector_e17c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("startsWith"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e17d -->
## Vector Drill E17d: Use `startsWith()` inside brackets

The vector `rx_codes` is provided. `startsWith(text, prefix)` returns a logical vector. Use it inside `[ ]` to return entries beginning with `RX`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e17d-setup, include=FALSE}
rx_codes <- c("RXA10", "TXA20", "RXB30", "RXA40", "QXA50")
```

```{r vector_e17d, exercise=TRUE, exercise.setup="vector_e17d-setup", topic="vector_indexing"}

```

```{r vector_e17d-solution}
rx_codes[startsWith(rx_codes, "RX")]
```

```{r vector_e17d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("startsWith"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e18a -->
## Vector Drill E18a: Use `is.na()` inside brackets

The vector `measurements` is provided. `is.na(values)` returns a logical vector indicating which values are missing. Use it inside `[ ]` to return all non-missing values. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e18a-setup, include=FALSE}
measurements <- c(4, NA, 12, 3, NA, 7)
```

```{r vector_e18a, exercise=TRUE, exercise.setup="vector_e18a-setup", topic="vector_indexing"}

```

```{r vector_e18a-solution}
measurements[!is.na(measurements)]
```

```{r vector_e18a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("is.na"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e18b -->
## Vector Drill E18b: Use `is.na()` inside brackets

The vector `STATUS` is provided. `is.na(values)` returns a logical vector indicating missing values. Use it inside `[ ]` to return only the non-missing status values. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e18b-setup, include=FALSE}
STATUS <- c("new", NA, "held", "done", NA)
```

```{r vector_e18b, exercise=TRUE, exercise.setup="vector_e18b-setup", topic="vector_indexing"}

```

```{r vector_e18b-solution}
STATUS[!is.na(STATUS)]
```

```{r vector_e18b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("is.na"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e18c -->
## Vector Drill E18c: Use `is.na()` inside brackets

The vector `lab.values` is provided. `is.na(values)` identifies missing values. Use it inside `[ ]` to return only the missing entries. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e18c-setup, include=FALSE}
lab.values <- c(1.2, NA, 2.8, 7.4, NA, 9.2)
```

```{r vector_e18c, exercise=TRUE, exercise.setup="vector_e18c-setup", topic="vector_indexing"}

```

```{r vector_e18c-solution}
lab.values[is.na(lab.values)]
```

```{r vector_e18c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("is.na"),
    min_brackets = 1
  )
})
```
<!-- /question -->

<!-- question: vector_e18d -->
## Vector Drill E18d: Use `is.na()` inside brackets

The vector `visit_days` is provided. `is.na(values)` returns a logical vector indicating missing values. Use it inside `[ ]` to return all non-missing visit days. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e18d-setup, include=FALSE}
visit_days <- c(2, 5, NA, 14, 20, NA, 35)
```

```{r vector_e18d, exercise=TRUE, exercise.setup="vector_e18d-setup", topic="vector_indexing"}

```

```{r vector_e18d-solution}
visit_days[!is.na(visit_days)]
```

```{r vector_e18d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = c("is.na"),
    min_brackets = 1
  )
})
```
<!-- /question -->
