<!-- question: vector_e11a -->
## Vector Drill E11a: Subvector of a subvector by position

The vector `scores` is provided. First take elements 2, 4, 6, and 8. From that subvector, return its third and first elements. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e11a-setup, include=FALSE}
scores <- c(10, 20, 30, 40, 50, 60, 70, 80)
```

```{r vector_e11a, exercise=TRUE, exercise.setup="vector_e11a-setup", topic="vector_indexing"}

```

```{r vector_e11a-solution}
scores[c(2, 4, 6, 8)][c(3, 1)]
```

```{r vector_e11a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 2
  )
})
```
<!-- /question -->

<!-- question: vector_e11b -->
## Vector Drill E11b: Subvector of a subvector by position

The vector `STATUS` is provided. First take elements 1, 3, 5, and 7. From that subvector, return its fourth and second elements. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e11b-setup, include=FALSE}
STATUS <- c("aa", "bb", "cc", "dd", "ee", "ff", "gg")
```

```{r vector_e11b, exercise=TRUE, exercise.setup="vector_e11b-setup", topic="vector_indexing"}

```

```{r vector_e11b-solution}
STATUS[c(1, 3, 5, 7)][c(4, 2)]
```

```{r vector_e11b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 2
  )
})
```
<!-- /question -->

<!-- question: vector_e11c -->
## Vector Drill E11c: Subvector of a subvector by position

The vector `lab.values` is provided. First take elements 3 through 8. From that subvector, return its fifth, second, and first elements. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e11c-setup, include=FALSE}
lab.values <- c(1.1, 2.2, 3.3, 4.4, 5.5, 6.6, 7.7, 8.8, 9.9)
```

```{r vector_e11c, exercise=TRUE, exercise.setup="vector_e11c-setup", topic="vector_indexing"}

```

```{r vector_e11c-solution}
lab.values[3:8][c(5, 2, 1)]
```

```{r vector_e11c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 2
  )
})
```
<!-- /question -->

<!-- question: vector_e11d -->
## Vector Drill E11d: Subvector of a subvector by position

The vector `visit_days` is provided. First take elements 2 through 7. From that subvector, return its sixth through third elements in reverse order. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e11d-setup, include=FALSE}
visit_days <- c(2, 5, 9, 14, 20, 27, 35, 44)
```

```{r vector_e11d, exercise=TRUE, exercise.setup="vector_e11d-setup", topic="vector_indexing"}

```

```{r vector_e11d-solution}
visit_days[2:7][6:3]
```

```{r vector_e11d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 2
  )
})
```
<!-- /question -->

<!-- question: vector_e12a -->
## Vector Drill E12a: Subvector of a subvector by name

The vector `rates` is provided. First take `beta`, `delta`, and `alpha`. From that subvector, return `delta` and `beta`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e12a-setup, include=FALSE}
rates <- c(alpha = 10, beta = 20, gamma = 30, delta = 40)
```

```{r vector_e12a, exercise=TRUE, exercise.setup="vector_e12a-setup", topic="vector_indexing"}

```

```{r vector_e12a-solution}
rates[c("beta", "delta", "alpha")][c("delta", "beta")]
```

```{r vector_e12a-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 2
  )
})
```
<!-- /question -->

<!-- question: vector_e12b -->
## Vector Drill E12b: Subvector of a subvector by name

The vector `STAFF` is provided. First take `owner`, `lead`, and `reviewer`. From that subvector, return `lead` and `owner`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e12b-setup, include=FALSE}
STAFF <- c(lead = "Ada", backup = "Grace", reviewer = "Rita", owner = "Lin")
```

```{r vector_e12b, exercise=TRUE, exercise.setup="vector_e12b-setup", topic="vector_indexing"}

```

```{r vector_e12b-solution}
STAFF[c("owner", "lead", "reviewer")][c("lead", "owner")]
```

```{r vector_e12b-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 2
  )
})
```
<!-- /question -->

<!-- question: vector_e12c -->
## Vector Drill E12c: Subvector of a subvector by name

The vector `lab.values` is provided. First take `calcium`, `sodium`, and `glucose`. From that subvector, return `glucose` and `calcium`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e12c-setup, include=FALSE}
lab.values <- c(glucose = 93, sodium = 140, potassium = 4.2, calcium = 9.4)
```

```{r vector_e12c, exercise=TRUE, exercise.setup="vector_e12c-setup", topic="vector_indexing"}

```

```{r vector_e12c-solution}
lab.values[c("calcium", "sodium", "glucose")][c("glucose", "calcium")]
```

```{r vector_e12c-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 2
  )
})
```
<!-- /question -->

<!-- question: vector_e12d -->
## Vector Drill E12d: Subvector of a subvector by name

The vector `status_flags` is provided. First take `archived`, `ready`, and `late`. From that subvector, return `late` and `archived`. Use single-bracket vector subscripting (`[ ]`).

```{r vector_e12d-setup, include=FALSE}
status_flags <- c(ready = TRUE, late = FALSE, reviewed = TRUE, archived = FALSE)
```

```{r vector_e12d, exercise=TRUE, exercise.setup="vector_e12d-setup", topic="vector_indexing"}

```

```{r vector_e12d-solution}
status_flags[c("archived", "ready", "late")][c("late", "archived")]
```

```{r vector_e12d-check}
grade_this({
  check_vector_subscript(
    code = .user_code,
    returned_value = .result,
    expected_value = .solution,
    required_calls = character(),
    min_brackets = 2
  )
})
```
<!-- /question -->
