# Data-frame subsetting drill bank

These chunks are intended to be pasted after the setup/logging/identity sections of the existing `learnr` tutorial.

They use only data frames from the standard `datasets` package that ships with R and is attached by default in a normal R session: `mtcars`, `iris`, `airquality`, `ToothGrowth`, `women`, `USArrests`, `PlantGrowth`, and `faithful`.

The drills intentionally distinguish among:

- `df[rows, columns]`
- one-dimensional data-frame indexing such as `df["column"]`
- `$`
- `[[ ]]`
- `drop = FALSE`
- `subset()`

The check chunks assume the existing helpers in `R/syntax_checkers.R`, particularly `uses_call()`, and the existing `gradethis` setup.

## Data-frame Drill DF_R01: First five rows

Using single-bracket data-frame subscripting (`[rows, columns]`) and `:`, return the first 5 rows of `mtcars`. Keep all columns.

```{r df_r01, exercise=TRUE}

```

```{r df_r01-solution}
mtcars[1:5, ]
```

```{r df_r01-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, ":")) {
    fail("Use the `:` operator as requested.")
  }
  if (!identical(.result, mtcars[1:5, ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R02: Selected row numbers

Using single-bracket subscripting and `c()`, return rows 2, 7, and 12 of `iris`, in that order. Keep all columns.

```{r df_r02, exercise=TRUE}

```

```{r df_r02-solution}
iris[c(2, 7, 12), ]
```

```{r df_r02-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, iris[c(2, 7, 12), ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R03: Contiguous middle rows

Using single-bracket subscripting and `:`, return rows 10 through 20 of `airquality`. Keep all columns.

```{r df_r03, exercise=TRUE}

```

```{r df_r03-solution}
airquality[10:20, ]
```

```{r df_r03-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, ":")) {
    fail("Use the `:` operator as requested.")
  }
  if (!identical(.result, airquality[10:20, ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R04: Exclude rows by number

Using single-bracket subscripting, return `women` with rows 1 and 15 omitted. Keep all columns.

```{r df_r04, exercise=TRUE}

```

```{r df_r04-solution}
women[-c(1, 15), ]
```

```{r df_r04-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, women[-c(1, 15), ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R05: Repeat and reorder rows

Using single-bracket subscripting and `c()`, return rows 3, 3, 1, and 5 of `PlantGrowth`, in exactly that order. Keep all columns.

```{r df_r05, exercise=TRUE}

```

```{r df_r05-solution}
PlantGrowth[c(3, 3, 1, 5), ]
```

```{r df_r05-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, PlantGrowth[c(3, 3, 1, 5), ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R06: Named rows

Using row names as character subscripts, return the rows `"Texas"`, `"Oregon"`, and `"Alabama"` from `USArrests`, in that order. Keep all columns.

```{r df_r06, exercise=TRUE}

```

```{r df_r06-solution}
USArrests[c("Texas", "Oregon", "Alabama"), ]
```

```{r df_r06-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, USArrests[c("Texas", "Oregon", "Alabama"), ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R07: Single named row

Using a row-name subscript, return the `"Datsun 710"` row of `mtcars` as a one-row data frame.

```{r df_r07, exercise=TRUE}

```

```{r df_r07-solution}
mtcars["Datsun 710", ]
```

```{r df_r07-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!identical(.result, mtcars["Datsun 710", ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R08: Rows matching one condition

Using single-bracket subscripting and a logical condition in the row position, return all rows of `mtcars` for cars with 4 cylinders.

```{r df_r08, exercise=TRUE}

```

```{r df_r08-solution}
mtcars[mtcars$cyl == 4, ]
```

```{r df_r08-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!identical(.result, mtcars[mtcars$cyl == 4, ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R09: Rows above a threshold

Using single-bracket subscripting and a logical condition, return all rows of `mtcars` with `mpg` at least 30.

```{r df_r09, exercise=TRUE}

```

```{r df_r09-solution}
mtcars[mtcars$mpg >= 30, ]
```

```{r df_r09-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, ">=")) {
    fail("Use `>=` as requested.")
  }
  if (!identical(.result, mtcars[mtcars$mpg >= 30, ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R10: Rows matching a character/factor value

Using single-bracket subscripting and a logical condition, return all rows of `iris` whose `Species` is `"virginica"`.

```{r df_r10, exercise=TRUE}

```

```{r df_r10-solution}
iris[iris$Species == "virginica", ]
```

```{r df_r10-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!identical(.result, iris[iris$Species == "virginica", ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R11: Rows matching two conditions

Using single-bracket subscripting, return rows of `ToothGrowth` where `supp` is `"OJ"` AND `dose` is 2.

```{r df_r11, exercise=TRUE}

```

```{r df_r11-solution}
ToothGrowth[ToothGrowth$supp == "OJ" & ToothGrowth$dose == 2, ]
```

```{r df_r11-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!identical(.result, ToothGrowth[ToothGrowth$supp == "OJ" & ToothGrowth$dose == 2, ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R12: Rows matching an OR condition

Using single-bracket subscripting, return rows of `women` where height is less than 60 OR greater than 70.

```{r df_r12, exercise=TRUE}

```

```{r df_r12-solution}
women[women$height < 60 | women$height > 70, ]
```

```{r df_r12-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "<")) {
    fail("Use `<` as requested.")
  }
  if (!uses_call(.user_code, "|")) {
    fail("Use `|` as requested.")
  }
  if (!uses_call(.user_code, ">")) {
    fail("Use `>` as requested.")
  }
  if (!identical(.result, women[women$height < 60 | women$height > 70, ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R13: Rows using %in%

Using single-bracket subscripting and `%in%`, return rows of `PlantGrowth` whose `group` is either `"trt1"` or `"trt2"`.

```{r df_r13, exercise=TRUE}

```

```{r df_r13-solution}
PlantGrowth[PlantGrowth$group %in% c("trt1", "trt2"), ]
```

```{r df_r13-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "%in%")) {
    fail("Use `%in%` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, PlantGrowth[PlantGrowth$group %in% c("trt1", "trt2"), ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R14: Remove missing values while filtering

Using single-bracket subscripting, return rows of `airquality` where `Ozone` is not missing and is greater than 100.

```{r df_r14, exercise=TRUE}

```

```{r df_r14-solution}
airquality[!is.na(airquality$Ozone) & airquality$Ozone > 100, ]
```

```{r df_r14-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "is.na")) {
    fail("Use `is.na` as requested.")
  }
  if (!uses_call(.user_code, "!")) {
    fail("Use `!` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!uses_call(.user_code, ">")) {
    fail("Use `>` as requested.")
  }
  if (!identical(.result, airquality[!is.na(airquality$Ozone) & airquality$Ozone > 100, ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R15: Logical recycling in the row subscript

Using the explicit logical subscript `c(TRUE, FALSE)` in the row position, return every other row of `women`, beginning with row 1. Keep all columns.

```{r df_r15, exercise=TRUE}

```

```{r df_r15-solution}
women[c(TRUE, FALSE), ]
```

```{r df_r15-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, women[c(TRUE, FALSE), ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_R16: Descending row order

Using single-bracket subscripting and `:`, return rows 10 down through 4 of `faithful`, in descending row order. Keep all columns.

```{r df_r16, exercise=TRUE}

```

```{r df_r16-solution}
faithful[10:4, ]
```

```{r df_r16-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, ":")) {
    fail("Use the `:` operator as requested.")
  }
  if (!identical(.result, faithful[10:4, ])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C01: First four columns as a data frame

Using single-bracket subscripting, return the first four columns of `mtcars` as a data frame.

```{r df_c01, exercise=TRUE}

```

```{r df_c01-solution}
mtcars[, 1:4]
```

```{r df_c01-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, ":")) {
    fail("Use the `:` operator as requested.")
  }
  if (!identical(.result, mtcars[, 1:4])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C02: Selected columns by number

Using single-bracket subscripting and `c()`, return columns 1, 6, and 9 of `mtcars`, in that order.

```{r df_c02, exercise=TRUE}

```

```{r df_c02-solution}
mtcars[, c(1, 6, 9)]
```

```{r df_c02-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, mtcars[, c(1, 6, 9)])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C03: Selected columns by name

Using single-bracket subscripting and a character vector of column names, return `mpg`, `wt`, and `hp` from `mtcars`, in that order.

```{r df_c03, exercise=TRUE}

```

```{r df_c03-solution}
mtcars[, c("mpg", "wt", "hp")]
```

```{r df_c03-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, mtcars[, c("mpg", "wt", "hp")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C04: Data-frame-style named column selection

Using the one-dimensional data-frame form `df[c("col1", "col2")]`, return the `Sepal.Length` and `Species` columns of `iris` as a data frame.

```{r df_c04, exercise=TRUE}

```

```{r df_c04-solution}
iris[c("Sepal.Length", "Species")]
```

```{r df_c04-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, iris[c("Sepal.Length", "Species")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C05: Reorder columns by name

Using single-bracket subscripting, return the columns of `women` in the order `weight`, then `height`.

```{r df_c05, exercise=TRUE}

```

```{r df_c05-solution}
women[, c("weight", "height")]
```

```{r df_c05-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, women[, c("weight", "height")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C06: Exclude one column by number

Using a negative numeric column subscript, return `iris` without its fifth column.

```{r df_c06, exercise=TRUE}

```

```{r df_c06-solution}
iris[, -5]
```

```{r df_c06-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!identical(.result, iris[, -5])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C07: Exclude several columns by number

Using a negative numeric column subscript and `c()`, return `mtcars` without columns 2, 8, and 10.

```{r df_c07, exercise=TRUE}

```

```{r df_c07-solution}
mtcars[, -c(2, 8, 10)]
```

```{r df_c07-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, mtcars[, -c(2, 8, 10)])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C08: Extract one column with $

Using `$`, extract and return the `Species` column of `iris` as a vector/factor, not as a one-column data frame.

```{r df_c08, exercise=TRUE}

```

```{r df_c08-solution}
iris$Species
```

```{r df_c08-check}
grade_this({
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!identical(.result, iris$Species)) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C09: Extract one named column with [[

Using `[[ ]]` with the column name, extract and return the `Ozone` column of `airquality` as a vector.

```{r df_c09, exercise=TRUE}

```

```{r df_c09-solution}
airquality[["Ozone"]]
```

```{r df_c09-check}
grade_this({
  if (!uses_call(.user_code, "[[")) {
    fail("Use double-bracket `[[ ]]` extraction as requested.")
  }
  if (!identical(.result, airquality[["Ozone"]])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C10: Extract one numbered column with [[

Using `[[ ]]` with a numeric subscript, extract and return the second column of `women` as a vector.

```{r df_c10, exercise=TRUE}

```

```{r df_c10-solution}
women[[2]]
```

```{r df_c10-check}
grade_this({
  if (!uses_call(.user_code, "[[")) {
    fail("Use double-bracket `[[ ]]` extraction as requested.")
  }
  if (!identical(.result, women[[2]])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C11: Single column with comma simplifies

Using `[, ]` with the character column name `"mpg"`, extract the `mpg` column of `mtcars` as a vector.

```{r df_c11, exercise=TRUE}

```

```{r df_c11-solution}
mtcars[, "mpg"]
```

```{r df_c11-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!identical(.result, mtcars[, "mpg"])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C12: Single column preserved as data frame

Using `[, ]` with `"mpg"` and `drop = FALSE`, return the `mpg` column of `mtcars` as a one-column data frame.

```{r df_c12, exercise=TRUE}

```

```{r df_c12-solution}
mtcars[, "mpg", drop = FALSE]
```

```{r df_c12-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_token(.user_code, "drop")) {
    fail("Include `drop` as requested.")
  }
  if (!identical(.result, mtcars[, "mpg", drop = FALSE])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C13: One-dimensional data-frame indexing preserves data frame

Using `df["column"]` syntax, return the `group` column of `PlantGrowth` as a one-column data frame.

```{r df_c13, exercise=TRUE}

```

```{r df_c13-solution}
PlantGrowth["group"]
```

```{r df_c13-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!identical(.result, PlantGrowth["group"])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C14: Reorder and repeat columns

Using single-bracket subscripting and column names, return `height`, `weight`, then `height` again from `women`, in that order.

```{r df_c14, exercise=TRUE}

```

```{r df_c14-solution}
women[, c("height", "weight", "height")]
```

```{r df_c14-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, women[, c("height", "weight", "height")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C15: Logical column subscript

Using the explicit logical column subscript `c(TRUE, FALSE, TRUE, FALSE)`, return the first and third columns of `USArrests`.

```{r df_c15, exercise=TRUE}

```

```{r df_c15-solution}
USArrests[, c(TRUE, FALSE, TRUE, FALSE)]
```

```{r df_c15-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, USArrests[, c(TRUE, FALSE, TRUE, FALSE)])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_C16: Column names from a different built-in data frame

Using single-bracket subscripting by name, return `eruptions` and then `waiting` from `faithful`.

```{r df_c16, exercise=TRUE}

```

```{r df_c16-solution}
faithful[, c("eruptions", "waiting")]
```

```{r df_c16-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, faithful[, c("eruptions", "waiting")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B01: Rows and columns by number

Using one single-bracket expression, return rows 1 through 6 and columns 1 through 3 of `mtcars`.

```{r df_b01, exercise=TRUE}

```

```{r df_b01-solution}
mtcars[1:6, 1:3]
```

```{r df_b01-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, ":")) {
    fail("Use the `:` operator as requested.")
  }
  if (!identical(.result, mtcars[1:6, 1:3])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B02: Rows by number, columns by name

Using one single-bracket expression, return rows 10 through 15 of `iris` and only `Sepal.Length` and `Petal.Length`.

```{r df_b02, exercise=TRUE}

```

```{r df_b02-solution}
iris[10:15, c("Sepal.Length", "Petal.Length")]
```

```{r df_b02-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, ":")) {
    fail("Use the `:` operator as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, iris[10:15, c("Sepal.Length", "Petal.Length")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B03: Named rows and named columns

Using row names and column names, return `Texas`, `California`, and `New York` from `USArrests`, with only `Murder` and `Assault`.

```{r df_b03, exercise=TRUE}

```

```{r df_b03-solution}
USArrests[c("Texas", "California", "New York"), c("Murder", "Assault")]
```

```{r df_b03-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, USArrests[c("Texas", "California", "New York"), c("Murder", "Assault")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B04: Logical rows and named columns

Using one single-bracket expression, return cars in `mtcars` with 6 cylinders, keeping only `mpg`, `hp`, and `wt`.

```{r df_b04, exercise=TRUE}

```

```{r df_b04-solution}
mtcars[mtcars$cyl == 6, c("mpg", "hp", "wt")]
```

```{r df_b04-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, mtcars[mtcars$cyl == 6, c("mpg", "hp", "wt")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B05: Factor condition and selected columns

Using one single-bracket expression, return only `Sepal.Width` and `Petal.Width` for `iris` rows whose `Species` is `"setosa"`.

```{r df_b05, exercise=TRUE}

```

```{r df_b05-solution}
iris[iris$Species == "setosa", c("Sepal.Width", "Petal.Width")]
```

```{r df_b05-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, iris[iris$Species == "setosa", c("Sepal.Width", "Petal.Width")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B06: Two conditions and selected columns

Using one single-bracket expression, return `len` and `dose` from `ToothGrowth` where `supp` is `"VC"` and `dose` is 1.

```{r df_b06, exercise=TRUE}

```

```{r df_b06-solution}
ToothGrowth[ToothGrowth$supp == "VC" & ToothGrowth$dose == 1, c("len", "dose")]
```

```{r df_b06-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, ToothGrowth[ToothGrowth$supp == "VC" & ToothGrowth$dose == 1, c("len", "dose")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B07: Threshold condition and reordered columns

Using one single-bracket expression, return rows of `women` with height at least 65, with columns ordered `weight`, then `height`.

```{r df_b07, exercise=TRUE}

```

```{r df_b07-solution}
women[women$height >= 65, c("weight", "height")]
```

```{r df_b07-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, ">=")) {
    fail("Use `>=` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, women[women$height >= 65, c("weight", "height")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B08: Missing-value-safe condition and selected columns

Using one single-bracket expression, return `Ozone`, `Temp`, and `Month` from `airquality` for rows where `Ozone` is not missing and is at least 80.

```{r df_b08, exercise=TRUE}

```

```{r df_b08-solution}
airquality[!is.na(airquality$Ozone) & airquality$Ozone >= 80, c("Ozone", "Temp", "Month")]
```

```{r df_b08-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "is.na")) {
    fail("Use `is.na` as requested.")
  }
  if (!uses_call(.user_code, "!")) {
    fail("Use `!` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!uses_call(.user_code, ">=")) {
    fail("Use `>=` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, airquality[!is.na(airquality$Ozone) & airquality$Ozone >= 80, c("Ozone", "Temp", "Month")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B09: Exclude rows and select columns

Using one single-bracket expression, omit the first 3 rows of `PlantGrowth` and keep only `weight` and `group`.

```{r df_b09, exercise=TRUE}

```

```{r df_b09-solution}
PlantGrowth[-c(1, 2, 3), c("weight", "group")]
```

```{r df_b09-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, PlantGrowth[-c(1, 2, 3), c("weight", "group")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B10: Reverse rows and columns

Using one single-bracket expression, return rows 8 down through 3 of `women`, with the columns in reverse order.

```{r df_b10, exercise=TRUE}

```

```{r df_b10-solution}
women[8:3, 2:1]
```

```{r df_b10-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, ":")) {
    fail("Use the `:` operator as requested.")
  }
  if (!identical(.result, women[8:3, 2:1])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B11: %in% rows and selected columns

Using one single-bracket expression and `%in%`, return `Murder` and `UrbanPop` for states whose row names are `"Alabama"`, `"Alaska"`, or `"Arizona"`.

```{r df_b11, exercise=TRUE}

```

```{r df_b11-solution}
USArrests[rownames(USArrests) %in% c("Alabama", "Alaska", "Arizona"), c("Murder", "UrbanPop")]
```

```{r df_b11-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "rownames")) {
    fail("Use `rownames` as requested.")
  }
  if (!uses_call(.user_code, "%in%")) {
    fail("Use `%in%` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, USArrests[rownames(USArrests) %in% c("Alabama", "Alaska", "Arizona"), c("Murder", "UrbanPop")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B12: OR condition and selected columns

Using one single-bracket expression, return `mpg` and `gear` for `mtcars` rows where `gear` is 3 OR 5.

```{r df_b12, exercise=TRUE}

```

```{r df_b12-solution}
mtcars[mtcars$gear == 3 | mtcars$gear == 5, c("mpg", "gear")]
```

```{r df_b12-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!uses_call(.user_code, "|")) {
    fail("Use `|` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, mtcars[mtcars$gear == 3 | mtcars$gear == 5, c("mpg", "gear")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B13: Compound numeric range

Using one single-bracket expression, return `height` and `weight` from `women` where height is between 62 and 68 inclusive.

```{r df_b13, exercise=TRUE}

```

```{r df_b13-solution}
women[women$height >= 62 & women$height <= 68, c("height", "weight")]
```

```{r df_b13-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, ">=")) {
    fail("Use `>=` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!uses_call(.user_code, "<=")) {
    fail("Use `<=` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, women[women$height >= 62 & women$height <= 68, c("height", "weight")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B14: Complete cases on selected variables

Using `complete.cases()` in the row subscript, return complete rows of `airquality` with respect to `Ozone` and `Solar.R`, and keep only `Ozone`, `Solar.R`, and `Temp`.

```{r df_b14, exercise=TRUE}

```

```{r df_b14-solution}
airquality[complete.cases(airquality[, c("Ozone", "Solar.R")]), c("Ozone", "Solar.R", "Temp")]
```

```{r df_b14-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "complete.cases")) {
    fail("Use `complete.cases` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, airquality[complete.cases(airquality[, c("Ozone", "Solar.R")]), c("Ozone", "Solar.R", "Temp")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B15: Repeated rows with selected columns

Using one single-bracket expression, return rows 1, 1, 4, and 2 of `faithful`, keeping the columns in the order `waiting`, then `eruptions`.

```{r df_b15, exercise=TRUE}

```

```{r df_b15-solution}
faithful[c(1, 1, 4, 2), c("waiting", "eruptions")]
```

```{r df_b15-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, faithful[c(1, 1, 4, 2), c("waiting", "eruptions")])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_B16: Select by condition and drop one column

Using one single-bracket expression, return `iris` rows with `Petal.Length` greater than 5, but omit the `Species` column by using a negative numeric column subscript.

```{r df_b16, exercise=TRUE}

```

```{r df_b16-solution}
iris[iris$Petal.Length > 5, -5]
```

```{r df_b16-check}
grade_this({
  if (!uses_call(.user_code, "[")) {
    fail("Use single-bracket `[` subsetting as requested.")
  }
  if (!uses_call(.user_code, "$")) {
    fail("Use `$` extraction as requested.")
  }
  if (!uses_call(.user_code, ">")) {
    fail("Use `>` as requested.")
  }
  if (!identical(.result, iris[iris$Petal.Length > 5, -5])) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S01: subset(): one condition

Using `subset()`, return all rows of `mtcars` with 6 cylinders.

```{r df_s01, exercise=TRUE}

```

```{r df_s01-solution}
subset(mtcars, cyl == 6)
```

```{r df_s01-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!identical(.result, subset(mtcars, cyl == 6))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S02: subset(): threshold

Using `subset()`, return rows of `mtcars` where `mpg` is greater than 25.

```{r df_s02, exercise=TRUE}

```

```{r df_s02-solution}
subset(mtcars, mpg > 25)
```

```{r df_s02-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, ">")) {
    fail("Use `>` as requested.")
  }
  if (!identical(.result, subset(mtcars, mpg > 25))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S03: subset(): select columns

Using `subset()`, return only `mpg`, `hp`, and `wt` from `mtcars`, without filtering rows.

```{r df_s03, exercise=TRUE}

```

```{r df_s03-solution}
subset(mtcars, select = c(mpg, hp, wt))
```

```{r df_s03-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!uses_token(.user_code, "select")) {
    fail("Include `select` as requested.")
  }
  if (!identical(.result, subset(mtcars, select = c(mpg, hp, wt)))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S04: subset(): filter and select

Using `subset()`, return cars with 4 cylinders and keep only `mpg`, `hp`, and `wt`.

```{r df_s04, exercise=TRUE}

```

```{r df_s04-solution}
subset(mtcars, cyl == 4, select = c(mpg, hp, wt))
```

```{r df_s04-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!uses_token(.user_code, "select")) {
    fail("Include `select` as requested.")
  }
  if (!identical(.result, subset(mtcars, cyl == 4, select = c(mpg, hp, wt)))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S05: subset(): factor value

Using `subset()`, return rows of `iris` whose `Species` is `"versicolor"`.

```{r df_s05, exercise=TRUE}

```

```{r df_s05-solution}
subset(iris, Species == "versicolor")
```

```{r df_s05-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!identical(.result, subset(iris, Species == "versicolor"))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S06: subset(): factor value and columns

Using `subset()`, return `Sepal.Length`, `Petal.Length`, and `Species` for `iris` rows whose `Species` is `"virginica"`.

```{r df_s06, exercise=TRUE}

```

```{r df_s06-solution}
subset(iris, Species == "virginica", select = c(Sepal.Length, Petal.Length, Species))
```

```{r df_s06-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!uses_token(.user_code, "select")) {
    fail("Include `select` as requested.")
  }
  if (!identical(.result, subset(iris, Species == "virginica", select = c(Sepal.Length, Petal.Length, Species)))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S07: subset(): two conditions

Using `subset()`, return rows of `ToothGrowth` where `supp` is `"OJ"` and `dose` is 0.5.

```{r df_s07, exercise=TRUE}

```

```{r df_s07-solution}
subset(ToothGrowth, supp == "OJ" & dose == 0.5)
```

```{r df_s07-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!identical(.result, subset(ToothGrowth, supp == "OJ" & dose == 0.5))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S08: subset(): two conditions and selected columns

Using `subset()`, return only `len` and `supp` from `ToothGrowth` where `dose` is 2 and `len` is greater than 25.

```{r df_s08, exercise=TRUE}

```

```{r df_s08-solution}
subset(ToothGrowth, dose == 2 & len > 25, select = c(len, supp))
```

```{r df_s08-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "==")) {
    fail("Use `==` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!uses_call(.user_code, ">")) {
    fail("Use `>` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!uses_token(.user_code, "select")) {
    fail("Include `select` as requested.")
  }
  if (!identical(.result, subset(ToothGrowth, dose == 2 & len > 25, select = c(len, supp)))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S09: subset(): missing-safe filter

Using `subset()`, return rows of `airquality` where `Ozone` is not missing and exceeds 80.

```{r df_s09, exercise=TRUE}

```

```{r df_s09-solution}
subset(airquality, !is.na(Ozone) & Ozone > 80)
```

```{r df_s09-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "is.na")) {
    fail("Use `is.na` as requested.")
  }
  if (!uses_call(.user_code, "!")) {
    fail("Use `!` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!uses_call(.user_code, ">")) {
    fail("Use `>` as requested.")
  }
  if (!identical(.result, subset(airquality, !is.na(Ozone) & Ozone > 80))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S10: subset(): missing-safe filter and select

Using `subset()`, return `Ozone`, `Temp`, and `Month` for `airquality` rows where `Ozone` is not missing and exceeds 80.

```{r df_s10, exercise=TRUE}

```

```{r df_s10-solution}
subset(airquality, !is.na(Ozone) & Ozone > 80, select = c(Ozone, Temp, Month))
```

```{r df_s10-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "is.na")) {
    fail("Use `is.na` as requested.")
  }
  if (!uses_call(.user_code, "!")) {
    fail("Use `!` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!uses_call(.user_code, ">")) {
    fail("Use `>` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!uses_token(.user_code, "select")) {
    fail("Include `select` as requested.")
  }
  if (!identical(.result, subset(airquality, !is.na(Ozone) & Ozone > 80, select = c(Ozone, Temp, Month)))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S11: subset(): numeric range

Using `subset()`, return rows of `women` where height is between 63 and 68 inclusive.

```{r df_s11, exercise=TRUE}

```

```{r df_s11-solution}
subset(women, height >= 63 & height <= 68)
```

```{r df_s11-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, ">=")) {
    fail("Use `>=` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!uses_call(.user_code, "<=")) {
    fail("Use `<=` as requested.")
  }
  if (!identical(.result, subset(women, height >= 63 & height <= 68))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S12: subset(): not equal

Using `subset()`, return rows of `PlantGrowth` whose `group` is not `"ctrl"`.

```{r df_s12, exercise=TRUE}

```

```{r df_s12-solution}
subset(PlantGrowth, group != "ctrl")
```

```{r df_s12-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "!=")) {
    fail("Use `!=` as requested.")
  }
  if (!identical(.result, subset(PlantGrowth, group != "ctrl"))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S13: subset(): %in%

Using `subset()` and `%in%`, return rows of `PlantGrowth` where `group` is `"ctrl"` or `"trt2"`.

```{r df_s13, exercise=TRUE}

```

```{r df_s13-solution}
subset(PlantGrowth, group %in% c("ctrl", "trt2"))
```

```{r df_s13-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, "%in%")) {
    fail("Use `%in%` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!identical(.result, subset(PlantGrowth, group %in% c("ctrl", "trt2")))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S14: subset(): state crime filter

Using `subset()`, return rows of `USArrests` where `Murder` is at least 10 and `UrbanPop` is below 70.

```{r df_s14, exercise=TRUE}

```

```{r df_s14-solution}
subset(USArrests, Murder >= 10 & UrbanPop < 70)
```

```{r df_s14-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, ">=")) {
    fail("Use `>=` as requested.")
  }
  if (!uses_call(.user_code, "&")) {
    fail("Use `&` as requested.")
  }
  if (!uses_call(.user_code, "<")) {
    fail("Use `<` as requested.")
  }
  if (!identical(.result, subset(USArrests, Murder >= 10 & UrbanPop < 70))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S15: subset(): state crime filter and select

Using `subset()`, return only `Murder` and `Assault` for `USArrests` rows where `Murder` is at least 10.

```{r df_s15, exercise=TRUE}

```

```{r df_s15-solution}
subset(USArrests, Murder >= 10, select = c(Murder, Assault))
```

```{r df_s15-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, ">=")) {
    fail("Use `>=` as requested.")
  }
  if (!uses_call(.user_code, "c")) {
    fail("Use `c()` as requested.")
  }
  if (!uses_token(.user_code, "select")) {
    fail("Include `select` as requested.")
  }
  if (!identical(.result, subset(USArrests, Murder >= 10, select = c(Murder, Assault)))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

## Data-frame Drill DF_S16: subset(): faithful threshold

Using `subset()`, return only the `eruptions` column of `faithful` for rows where `waiting` exceeds 80. Preserve the result as a data frame.

```{r df_s16, exercise=TRUE}

```

```{r df_s16-solution}
subset(faithful, waiting > 80, select = eruptions)
```

```{r df_s16-check}
grade_this({
  if (!uses_call(.user_code, "subset")) {
    fail("Use `subset()` as requested.")
  }
  if (!uses_call(.user_code, ">")) {
    fail("Use `>` as requested.")
  }
  if (!uses_token(.user_code, "select")) {
    fail("Include `select` as requested.")
  }
  if (!identical(.result, subset(faithful, waiting > 80, select = eruptions))) {
    fail("The returned object does not exactly match the requested result.")
  }
  pass("Correct.")
})
```

