# Vector creation and subscripting drill bank

This bank drills vector creation, assignment, and single-bracket vector subscripting. Construction questions always assign the new vector to a specified variable and return that variable. Subscript checkers deliberately allow any valid expression inside `[ ]` unless the prompt explicitly names a function or operator that must be practiced.

Authoring policy for this bank:

- do not drill integer `L` suffixes, complex numbers, scientific notation, zero subscripts, logical recycling, duplicate names, names containing spaces, typed `NA_*` constants, or name preservation during subscripting;
- use variable names of at least two characters and vary naming styles, including uppercase, lowercase, dots, and underscores;
- accept `T`/`F` anywhere `TRUE`/`FALSE` would work;
- use plain `NA` for missing values;
- include repeated subsetting of subvectors and functions that return vectors for use inside brackets;
- each logic family has four literal variants (`a` through `d`).

The canonical question blocks are split into child files under `question-bank/vector_drills/` to keep this large bank maintainable. Rendering this file includes all of them in the student-style `learnr` interface.

```{r vector-drill-child-paths, include=FALSE}
vector_drill_candidates <- c(
  file.path("question-bank", "vector_drills"),
  "vector_drills"
)
vector_drill_dir <- vector_drill_candidates[
  dir.exists(vector_drill_candidates)
][1]

if (is.na(vector_drill_dir)) {
  stop("Could not locate the vector drill child files.")
}

vector_drill_children <- file.path(
  vector_drill_dir,
  c(
    "creation_basic.Rmd",
    "creation_sequences.Rmd",
    "creation_named.Rmd",
    "creation_missing.Rmd",
    "creation_misc.Rmd",
    "indexing_positions.Rmd",
    "indexing_omit_logical.Rmd",
    "indexing_names.Rmd",
    "indexing_nested.Rmd",
    "indexing_which_grep.Rmd",
    "indexing_match_order.Rmd",
    "indexing_string_missing.Rmd",
    "indexing_membership_sequence.Rmd"
  )
)
```

```{r vector-drill-children, child=vector_drill_children}
```
