---
title: "Topic Metadata Example"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
```

## Tagged scored exercise

Return the third element of `letters` using single-bracket indexing.

`topic` is stored in the generated question manifest. Because `points` is
omitted, this `exercise=TRUE` chunk is worth 1 point.

```{r vector_index_example, exercise=TRUE, topic="vector_indexing"}

```

```{r vector_index_example-solution}
letters[3]
```

```{r vector_index_example-check}
grade_this({
  if (!identical(.result, letters[3])) fail("Return the third element of `letters`.")
  pass("Correct.")
})
```

## Untagged practice exercise

Return `1 + 1`. Because this exercise has no `topic` chunk option, the manifest
builder assigns it the topic `unassigned` and emits a warning. `points=0` keeps
it in the event log but excludes it from the gradebook.

```{r untagged_example, exercise=TRUE, points=0}

```

```{r untagged_example-solution}
1 + 1
```

```{r untagged_example-check}
grade_this({
  if (!identical(.result, 2)) fail("Return 1 + 1.")
  pass("Correct.")
})
```
